Rule Synthesis for Rule-based Intrusion Detectors

### 2020-06-03 paper/paper.tex
pass IV.C5

\subsubsection{Weight Optimization}
\label{sec:weight-optimization}
A key strategy for obtaining the ideal ranking lie in finding optimal weights
for the heuristic functions. The ranking of a golden rule, for a set of $N$ 
attacks, is given by $R(W) = \sum_{i=1}^{N}\mathit{R_i}$, where 
$R_i = (w_1 \cdot popt) \cdot (w_2 \cdot ncont) \cdot (w_3 \cdot pcont) \cdot (w_4 \cdot phttp)$
and $W = \langle{}w_1, w_2, w_3, w_4\rangle{}$ are the weights considered for each heuristic.
%
In  order to compute the optimal weights, we used the Differential Evolution 
algorithm from SciPy\cite{diff-evo-scipy}.
The optmization consists in minimizing the function of every attack's golden rule 
ranking in our set given a combination of weights. Formally, $W  = \displaystyle \argmin_W R$.
%
The algorithm also takes as input the range of the weights (between 0 and 1) 
and the max number of generations, which we set to 10 (confirmation whether 
this number suffices remains to future work). The weights are 
as follows $\langle{}0.280, 0.057, 0.043, 0.490\rangle{}$.

>>>>

\subsubsection{Weight Optimization}
\label{sec:weight-optimization}
A key strategy for obtaining the ideal ranking lie in finding optimal weights
for the heuristic functions. The sum of $R_i$ rankings of the golden rules, for a set of $N$ 
attacks, is given by $R(W) = \sum_{i=1}^{N}\mathit{R_i}$, where $W = \langle{}w_1, w_2, w_3, w_4\rangle{}$ are the weights considered for each heuristic.
%
In  order to compute the optimal weights, we used the Differential Evolution 
algorithm from SciPy\cite{diff-evo-scipy}.
The optmization consists in minimizing the function of every attack's golden rule 
ranking in our set given a combination of weights. Formally, $W  = \displaystyle \argmin_W R$.
%
The algorithm also takes as input the range of the weights (between 0 and 1) 
and the max number of generations, which we set to 10 (confirmation whether 
this number suffices remains to future work). The weights are 
as follows $\langle{}0.280, 0.057, 0.043, 0.490\rangle{}$.
